Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-01 ongoing/report/article.tex
Express as SOCP

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[linkcolor=blue]{hyperref}
\usepackage{xcolor}
\usepackage[ocgcolorlinks]{ocgx2}

@@

@@

We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.

Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
But that knowledge is hardly always available.
What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).

Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithm also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus in need.

@@

\Result
{Definition}
{
\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \{\mathrm{supp}(x)\} \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
\mathrm{s.t.} \quad Ax =y
\end{gather}
}

@@

\Result
{Notation}
{
Let \(T \subset \mathbb{N}\).
Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
}

\Result
{Definition}.
{
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|\theta\|^2
\leq \|X_T \theta\|_2^2
\leq (1+\delta_S) \|\theta\|^2
\end{gather}
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
\begin{gather}
| \langle X_T c, X_{T'} c' \rangle |
\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather}

@@

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
\begin{gather}
   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp(-n c_0(\epsilon))
\end{gather}
where we have
\begin{gather}
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
\end{gather}
}

@@

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
\begin{gather}
y[t] =(x[t] \star h[t]) +z[t]
\end{gather}
where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
\begin{gather}
y =X h
\end{gather}
where \(X\) takes the form
\begin{align}
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
\end{align}
We seek to get \(h\) in this undertermined system.

@@

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

@@

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
\begin{gather}
y =WHF x
\end{gather}

\Result
{Definition}
{
Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
}

\Result
{Definition.}
{
For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
}

With (), scholars often exploit the relation
\begin{gather}
\mathrm{vec}(Y)
=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
\end{gather}

@@

We restrict our consideration to the uniform linear array, which can be modeled as
\begin{gather}
\mathbf{a}(\phi')
=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
\end{gather}
where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
\end{gather}
The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.

For our purpose, we may absorb the argument of \(\mathbf{a}\) as
\begin{gather}
\phi_l
=\frac{d}{\lambda} \sin \phi_l' \\
\theta_l
=\frac{d}{\lambda} \sin \theta_l'
\end{gather}
to get a simpler form
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
\end{gather}

Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.

\Result
{Definition.}
{
Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
\begin{gather}
\mathbf{u} =\dagger F \mathbf{v}
\end{gather}
where each entry of the matrix \(K\) is defined to be
\begin{gather}
   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
\quad m,n =0,1,2,\dotsc, N-1
\end{gather}
where \(i =\sqrt{-1}\).
}

@@

We consider the situation with a hybrid structure at both transmitter and receiver end.
Each end consists of both digital and analog percoders and combiners.
In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
Recall that analog precoder is restricted to have value with magnitude being unity.
To set up notation, we list them as below.
\begin{gather}
F_B \in \mathbb{R}^{N_r \cdot N_s} \\
F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
F_B \in \mathbb{R}^{N_r \cdot N_h} \\
F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
\end{gather}
And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.

In summary, the effective channel may be written as
\begin{gather}
U (\omega_h, \omega_e)
:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
\end{gather}
Supress the probabilistic index for simplicity, we restate the same equation as
\begin{gather}
Y
:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
\end{gather}

@@

The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
\begin{gather}
Y_{:,n}
:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
n =1, 2, \dotsc, N_B
\end{gather}
The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.

Following previous work on CSS, we write
\begin{gather}
h := \mathrm{vec}(H) \\
u := \mathrm{vec}(U) \\
A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
\end{gather}
to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
What shall we do?

Observe that, if we write
\begin{gather}
G =K^\dagger H
\end{gather}
as the spatial frequency domain representation of \(H\), then
\begin{gather}
Y
:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
n =1, 2, \dotsc, N_B
\end{gather}
If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
\begin{gather}
\mathrm{vec}(Y)
\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
\end{gather}
To simplify notation, set 
\begin{gather}
P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
\end{gather}
The instances of \(P\) is completely determined in the transmitter and receiver end, that is
\begin{gather}
P =P(\omega_t, \omega_r)
\end{gather}
If so, our program reads

\Result
{Program}
{
Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(U\) is the acquired effective channel matrix under noisy observation.
\(A\) is defined just above in ().
Set
\begin{gather}
r =u -P h
\end{gather}
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{g}
=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{g}\) back to the space domain as
\begin{gather}
\hat{h}
=K^\dagger \hat{g}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\mathrm{vec}^{-1} (\hat{h})
\end{gather}
}

It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.

@@

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.

We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

Consider
\begin{gather}
d =g -\hat{g}
\end{gather}
And let
\begin{itemize}
\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
\end{itemize}
So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
\begin{gather}
\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
A \cup B \cup C =\{1, \dotsc, N\}.
\end{gather}

\Result
{Lemma.}
{
Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
\begin{gather}
\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
\end{gather}

To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
\begin{align}
S(\phi)
:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
\quad 0 \leq \phi \leq \pi
\end{align}
By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
\begin{align}
S(\phi)
\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
=& \frac{-48}{\phi^3 -24\phi}
\quad 0 \leq \phi \leq \pi,
\end{align}

The fraction above can be bounded.

>>>>

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[linkcolor=blue]{hyperref}
\usepackage{xcolor}
\usepackage[ocgcolorlinks]{ocgx2}
\usepackage{stackengine}

@@

\newcommand{\MB}[1]{\mathbb{#1}}
\newcommand{\MC}[1]{\mathcal{#1}}
\newcommand{\MF}[1]{\mathfrak{#1}}
\newcommand{\RM}[1]{\mathrm{#1}}
\newcommand{\T}[1]{\tilde{#1}}
\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
\newcommand{\M}[1]{\V{\V{#1}}}

\newcommand{\LA}{\langle}
\newcommand{\RA}{\rangle}

@@

We restrict our discussion to the Hilbert space over the field of \(\MB{R}\) or \(\MB{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
To avoid being too pedantic, we simply write \(\V{a} \in \MB{C}^N\) to stress \(\V{a}\) is a \(N\)-dimensional vector, and the role it plays in the vector space is understood.
Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
Inner product is denoted as \(\LA \MB{a}, \MB{b} \RA\).
Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Especially, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).

\(|a|\) denotes the magnitude for real or complex numbers.
\(\|\V{a}\|_p\) denotes the \(\ell_\infty\)-norm of \(\V{a}\).
Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.
The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(\MF{Re}(a) +i \MF{Im}(a)\)

Denote as \(\MB{P}(X)\) the probability, \(\MB{E}(X)\) the expectation, \(\MB{Var}(X)\) the variance.
Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\MB{P}\) and \(\MB{E}\).

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\RM{SNR})\).
But that knowledge is hardly always available.
What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).

Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithm also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus in need.

@@

\Result
{Definition}
{
\(x \in \MB{K}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \{\RM{supp}(x)\} \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\RM{min}_{x' \in \MB{R}^K} \quad \|x'\|_1
\RM{s.t.} \quad Ax =y
\end{gather}
}

@@

\Result
{Notation}
{
Let \(T \subset \MB{N}\).
Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
}

\Result
{Definition}.
{
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\vartheta\) with \(\|\vartheta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|\vartheta\|^2
\leq \|X_T \vartheta\|_2^2
\leq (1+\delta_S) \|\vartheta\|^2
\end{gather}
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\vartheta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
\begin{gather}
| \LA X_T c, X_{T'} c' \RA |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather}

@@

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
\RM{subject}\; \RM{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \MB{V}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
\begin{gather}
   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp(-n c_0(\epsilon))
\end{gather}
where we have
\begin{gather}
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
\end{gather}
}

@@

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
\begin{gather}
y[t] =(x[t] \star h[t]) +z[t]
\end{gather}
where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
\begin{gather}
y =X h
\end{gather}
where \(X\) takes the form
\begin{align}
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
\end{align}
We seek to get \(h\) in this undertermined system.

@@

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \MB{V}(M)\), \(x \in \MB{V}(N)\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

@@

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
\begin{gather}
   \V{y} =\M{W} \M{H} \M{F} \V{x}
\end{gather}

\Result
{Definition}
{
Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}(n,m)\).
}

\Result
{Definition.}
{
For \(\RM{vec}(A) \in \MB{M}(n,m)\) and \(\RM{vec}(A) \in \MB{M}(n,m)\)
Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
}

With (), scholars often exploit the relation
\begin{gather}
\RM{vec}(Y)
=\big[ (F^\dagger) \otimes W \big] \RM{vec}(\M{H})
\end{gather}

@@

We restrict our consideration to the uniform linear array, which can be modeled as
\begin{gather}
\V{a}(\varphi')
=\sum_{n=1}^{N} \RM{e}^{n \varphi' i} \V{u}_n
\end{gather}
where \(i\) is the imaginary unit, \(\V{u}_n\) is the unit vector of the \(n\)-th component.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\dagger
\end{gather}
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
\begin{gather}
\varphi_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l'
\end{gather}
to get a simpler form
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\dagger
\end{gather}

\Result
{Definition.}
{
}

@@

We consider the situation with a hybrid structure at both transmitter and receiver end.
Each end consists of both digital and analog percoders and combiners.
In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
To set up notation, we list them as below.
\begin{gather}
F_B \in \MB{C}^{N_r \cdot N_y} \\
F_R \in \MB{C}^{N_h \cdot N_r} \\
F_B \in \MB{C}^{N_r \cdot N_h} \\
F_B \in \MB{C}^{N_y \cdot N_r}.
\end{gather}
Recall that analog precoder is restricted to have value with magnitude being unity.
\begin{gather}
 |F_R(n_1,n_2)| =1, \quad
 n_1 =1, \dotsc N_h, \quad
n_2 =1, \dotsc N_r \\
 |W_R(n_1,n_2)| =1, \quad
 n_1 =1, \dotsc N_r, \quad
n_2 =1, \dotsc N_h
\end{gather}

And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.

In summary, the effective channel may be written as
\begin{gather}
Y (\omega_h, \omega_e)
:=W_B(\omega_r) W_R(\omega_r) ( H(\omega_h) F_R(\omega_t) F_B(\omega_t) +Z(\omega_z) )
\end{gather}
Supress the event space index for brevity, we restate the same equation as
\begin{gather}
Y
:=W_B W_R ( H F_R F_B +z )
\end{gather}

@@

The effective channel \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
\begin{gather}
\M{Y}(:,n)
:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_m +\V{z} ), \quad
n =1, 2, \dotsc, N_y
\end{gather}
The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), and of course \(\M{W}_R, \M{W}_B, \M{F}_R, \M{F}_B\) which are in our control.

Following previous work on CSS, we write
\begin{gather}
\V{h} := \RM{vec}(\M{H}) \\
\V{y} := \RM{vec}(\M{Y}) \\
\M{P}' :=(\M{F}_R \M{F}_B) \otimes (\M{W}_B \M{W}_R)
\end{gather}
to formulate our goal as sparse recovery problem of \(\RM{vec}(H)\) to be
\begin{gather}
\V{y} =\M{P}' \V{h} +\V{z}
\end{gather}
But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
What shall we do?

Introduce the discrete Fourier matrix \(K\) defined to be
\begin{gather}
\M{K} \in \MB{M}(N_h, N_h) \\
\M{K}(n_1, n_2) =\frac{1}{\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N},
\quad n_1, n_2 =0,1,2,\dotsc, N-1
\end{gather}
where \(i =\sqrt{-1}\).
And observe that, if we write
\begin{gather}
\M{G}
=\M{K}^\dagger \M{H}
\end{gather}
which has the interpretation as the spatial frequency domain representation of \(H\), then
\begin{gather}
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\dagger \M{Z} )
\end{gather}
If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
\begin{gather}
\RM{vec}(Y)
\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \RM{vec}(H)
\end{gather}
To simplify notation, set 
\begin{gather}
P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
\end{gather}
The instances of \(P\) is completely determined in the transmitter and receiver end, that is
\begin{gather}
P =P(\omega_t, \omega_r)
\end{gather}
If so, our program reads

\Result
{Program}
{
Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(Y\) is the acquired effective channel matrix under corruption of noise \(z\).
\(P\) is defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{g}
=\underset {{h}} {\RM{min}} \|h\|_1 \quad
\RM{s.t.}\;\; \|P^\dagger (y -P h)\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{g}\) back to the space domain as
\begin{gather}
\hat{h}
=K \hat{g}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\RM{vec}^{-1} (\hat{h})
\end{gather}
}

It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.

@@

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

Consider
\begin{gather}
d =g -\hat{g}
\end{gather}
And let
\begin{itemize}
\item \(\MC{A}\) be the largest \(L\) position of \(g\).
\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
\end{itemize}
So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
\begin{gather}
\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
   \MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
\MC{A} \cup \MC{C} \cup \MC{C} =\{1, \dotsc, N\}.
\end{gather}

\Result
{Lemma.}
{
Let \(\varphi(\omega_h)\) and \(\vartheta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
\begin{gather}
\|g_{\MC{A}}\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
\end{gather}
}

To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
\begin{align}
D(\varphi)
:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi} \right| \\ \notag
=&\frac{|\sin(N \varphi/2)|}{|\sin(\varphi /2)|},
\quad 0 \leq \varphi \leq \pi
\end{align}
where \(\RM{e}\) is the base of natural logarithm, and \(i =\sqrt{-1}\).

By taking the first two term of the expansion
\begin{align}
\sin x =x -x^3/6 + \MC{O}(x^5), \quad x \ll 1
\end{align}
and noting the monotony of the first two terms,
\begin{align}
D(\varphi)
\leq& \frac{1}{\varphi/2 -(\varphi/2)^3/6} \notag \\
=& \frac{-48}{\varphi^3 -24\varphi}
\quad 0 \leq \varphi \leq \pi,
\end{align}
The fraction above can be bounded.
